\thetitle

### 2008-06-04 paper.tex
Work on related work & motivation.

\newcommand{\FHC}{Hern\'andez-Campos~\textit{et~al.}}
\newcommand{\class}[1]{\textsc{#1}}
\newcommand{\model}[1]{\textsf{#1}}
\newcommand{\RFC}[1]{\caps{RFC}~{#1}}

@@

To address the question of whether there are better ways to reduce the dimensionality of network behaviors, we first make a simple observation.
In linear representations of traffic, uniform, marginal and conditional assumptions are assertions about rows and columns of the representation matrix being identical. 
Moreover, real traffic matrices can be transformed into uniform, marginal or conditional forms through  very simple matrix multiplications.
These transformations, however, are extremely destructive: the matrices are degenerate with very low rank,\ranknote so multiplication destroys almost all information in the original traffic matrix.

@@

We argue that matrix factorization, which is nondestructive, is a far superior way to reduce the dimensionality of network traffic behaviors.
% To show how traffic can be modeled less destructively, 
% To demonstrate how linear representation allows drastically improved analysis and modeling of network traffic,
To demonstrate this approach, we use non-negative matrix factorization (\caps{NMF}) to find a low-dimensional approximation of the packet size and inter-packet interval behavior matrices.
% As an example of how the linear representation allows drastically improved analysis and modeling of network traffic, we apply non-negative matrix factorization to find an low-dimensional representation of packet size and inter-packet flow behaviors.
% Each flow's behavior can be explained as a linear combination of only twelve ``basic behaviors.'' 
% Although they are found purely algorithmically from packet size and inter-packet interval distributions, these behaviors correspond to intuitive mode of network activity.
This factorization extracts a small set of ``basic behaviors'' from a traffic matrix and simultaneously explains each flow's observed behavior as a mixture of these basic behaviors.
Although the basic behaviors are found algorithmically, they correspond to intuitive network activities such as file transfer, typing via \caps{SSH}, web surfing, and ping traffic.

@@

The rest of the paper is organized as follows. In \Section{motivation} we discuss motivation and related work. The General Matrix Model is presented in \Section{general-matrix-model}. In Sections~\ref{sec:common-properties}~and~\ref{sec:modeling-concepts} we explore how common network properties and modeling concepts can be expressed in the the \caps{GMM} framework. Our experimental and analytical methodology for evaluating traffic models is presented in \Section{methodology}, while the results of our experiments are explained and analyzed in \Section{results}. The ramifications of these results are discussed in \Section{discussion}. Finally, in \Section{conclusions}, we conclude with a discussion of how this research may be applied to current wireless studies. %, and how it points the way to better traffic models for the future.

@@

The interaction of network users and application behavior with the lower layers of the networking stack is characterized by where, when, how much, and to whom data is transmitted. The joint pattern of traffic generation and mobility through time and space completely determines the effect of wireless usage on the lower levels of the network. This is due to the data-agnostic nature of the protocol stack: by design, \caps{IP} networks treat all data in the same manner~\cite{Clark88}.\QoSnote The credibility of conclusions derived from simulation or experimental deployment depends crucially on our confidence that the models used to generate traffic in experiments are sufficiently realistic. \Figure{trace-vs-uniform} demonstrates how drastically different network traffic appears when assumptions of uniform behavior at various levels are imposed. Assumptions of independence are not as visually dramatic, but we will demonstrate that they distort the performance characteristics of networks almost as much or more than uniform models.

Paxson and Floyd observed~\cite{Paxson95} that the interplay between endpoint behavior and the network conditions is inherently \textit{closed-loop} in the sense that it is potentially affected by complex feedback. Traffic models typically attempt to preserve the closed-loop behavior of network traffic~\cite{Avallone04,Hernandez06:dissertation}. This presents a fundamental difficulty, however, in that it presumes that we know the intent of endpoints: what \textit{would} they have done under different conditions? While we can speculate about what an individual node might hypothetically do, we currently hardly understand the impact of the full-network traffic pattern upon performance metrics at all---even without trying to account for hypothetical reactions to alternate situations. A fuller understanding of total network behavior must be reached before we can sensibly tackle the complexities of multi-level behavioral feedback. Accordingly, in this paper we attempt to provide a first-order approximation of complete network behavior by studying the response of performance metrics to \textit{open-loop} traffic models without multi-level feedback. It is important to realize that while this does not provide a final picture, we currently lack even a first-order understanding of the effect of different workloads on performance. This first-order understanding is an essential initial step.

@@

The simplifying assumptions made by most traffic models can be classified into three categories. We use the terms \textit{uniformity}, \textit{marginality}, and \textit{regularity} to describe these classes of assumptions. They are all assumptions about the ``sameness'' of aspects of network behaviors; they differ, however, in whether the make stipulations about uniformity within each flow, across all flows, or within groups of flows. In the following sections, we explore how various modeling concepts can be expressed in the framework of the General Matrix Model. Models are expressed as transformations that will convert arbitrary traffic matrix instances into similar ones that satisfy the model's assumptions. These transformations will later allow us to evaluate the effect of each model's simplifications on the realism of generated workloads.

@@

%How do marginal models translate into the algebraic language of the General Matrix Model? Whereas uniformity assumptions for nodes,

@@

The first model we evaluate is the General Matrix Model itself. We derive the matrix representation directly from the trace data and use it to generate workload as described in \Section{traffic-generation}. This serves to test whether the \caps{GMM} is sufficiently general: if it accurately reproduces all performance metrics across the collection of scenarios simulated, this provides strong evidence that \caps{GMM} captures enough of the detail of trace behavior to be considered a sufficiently general representation of network traffic patterns. %An affirmation of the generality of the \caps{GMM} acts as reduction of the

@@

%The original trace traffic serves as a control group against which to compare all other models. Before we can evaluate the General Matrix Model (\caps{GMM}), we must establish that one potentially important aspect of traffic behavior that is \textit{not} represented in the \caps{GMM} can legitimately be discarded. That aspect of behavior is \textit{\caps{TCP} feedback}. The \caps{GMM} does not specify the \caps{IP} protocol type of each flow. Therefore we must establish the extent to which using \caps{UDP} flows, without reliable delivery or congestion control, affects performance metrics.
%%\caps{GMM} also does not indicate which flows are paired with each other in a client-server relationship. While this pairing does not affect non-\caps{TCP} flows, we implement.
%Other synthetic models derived from algebraic transformations of the \caps{GMM} are listed in \Table{traffic-models}.

@@

Our general methodology is to compare performance metrics in simulations using real traffic patterns from traces to the same metrics in simulations using a variety of trace-based models and synthetic traffic models defined using the General Matrix Model. We use a 24-hour trace recorded in an infrastructured 802.11g wireless \caps{LAN} with 18 access points, deployed at the 60th Internet Engineering Task Force meeting (\caps{IETF}60), held in San Diego during August of 2004. The traffic trace was captured using \texttt{\small{tcpdump}} at a single router, through which all wireless traffic for the meeting was routed, including traffic between wireless nodes. The snap length of the capture was 100 bytes, allowing \caps{IP}, \caps{ICMP}, \caps{UDP} and \caps{TCP} headers to be analyzed. We limit our work to the 24-hour sub-trace recorded on Wednesday, August 4th. This trace contains a broad variety of behaviors and entails a very large volume of traffic: 2.1 million flows, 58 million packets, and 52 billion bytes.
% 2,085,563 flows, 58,377,994 packets of application data, and 51,988,245,537 bytes of application data.

@@

What would better traffic models look like? How can we create them? One possible approach is to use actual traffic traces as we have done. This approach is unsatisfactory, however, because it provides the experimenter with almost no control over experiments. Synthetic models have parameters, which can be tweaked as necessary---adjusting, for example, the number of active nodes in a simulation, without affecting other parameters. Traffic traces, on the other hand, must be used without significant alteration if they are to actually provide the desired realism. This inability to control all but one or two parameters is nearly crippling for experimental purposes. Therefore, the research community needs models whose parameters can be adjusted independently, but whose performance characteristics can be made to resemble whatever example of network behavior one might need. The General Matrix Model does not yet fulfill this role since its parameters cannot be freely varied. We believe, however, that \caps{GMM} plays a vital role in the ongoing process of developing  of better models. By reducing the general problem of traffic modeling to the domain of linear algebra, we have provided traffic researchers with a vast array of powerful theoretical and computational tools that can be immediately applied to the problem at hand.\footnote{The derived models used in this paper were all implemented in Matlab, each in only a few simple lines. All the models used here are implemented in only 19 total lines of code. Of course, the framework to apply them to traffic traces and simulations is somewhat larger.} What are the next steps? The authors are currently investigating a variety of matrix factorization and clustering techniques to extract hidden structure from a large and diverse body of real traffic.

@@

We have presented a fundamentally new, algebraic way of representing traffic patterns in local area networks. We call this representation the General Matrix Model. Each flow of a traffic collection is represented as a single high-dimensional vector with components representing the \caps{IP} protocol type, source and destination nodes, start time, flow size, and packet behavior. The essential property of the algebraic representation is that standard vector operations compute natural and useful descriptions of aggregate behavior over the collection of flows represented. Our experimental validation demonstrates clearly that the General Matrix Model accurately reproduces the performance characteristics of of real traffic. The benefits of a performance-preserving algebraic representation are multifold. The algebraic forms of the simplifying assumptions made by many common modeling approaches provide unprecedented clarity and coherence to a complex and confusing subject. For example, assumptions that various aspects of flow behavior are stochastically or deterministically uniform all take the same form algebraically: left matrix multiplication. The other major class of common simplifying assumptions made by traffic models is to apply some marginal behavior across the entire collection of flows or to disjoint subsets of the flows. Such simplifications correspond to right matrix multiplication in \caps{GMM}. Because of the simplicity and clarity that the algebraic structure brings to the subject, we can see clearly now that both common types of simplifying assumptions are na\"ive and simplistic. Our experimental results bolster this conclusion: both uniform and marginal models significantly misrepresent many important network performance metrics. With the General Matrix Model, however, we stand poised to use the powerful tools of modern linear algebra to develop general, elegant and powerful models of network behavior that just work.

>>>>

\newcommand{\FHC}{Hern\'andez-Campos~\textit{et~al.}}
\newcommand{\class}[1]{\textsc{#1}}
\newcommand{\model}[1]{\textsf{#1}}
\newcommand{\RFC}[1]{\caps{RFC}~{#1}}
\newcommand{\tmix}{T\caps{MIX}}

@@

To address the question of whether there are better ways to reduce the dimensionality of network behaviors, we first make a simple observation.
In linear representations of traffic, uniform, marginal and conditional assumptions are assertions about rows and columns of the representation matrix being identical. 
Moreover, real traffic matrices can be transformed into uniform, marginal or conditional forms through  very simple matrix multiplications.
These transformations, however, are extremely destructive: the matrices are degenerate with very low rank, so multiplication destroys almost all information in the original traffic matrix.

@@

We argue that matrix factorization, which is nondestructive, is a far superior to multiplication as a way to reduce the dimensionality of network traffic behaviors.
% To show how traffic can be modeled less destructively, 
% To demonstrate how linear representation allows drastically improved analysis and modeling of network traffic,
To demonstrate this approach, we use non-negative matrix factorization (\caps{NMF}) to find a low-dimensional approximation of the packet size and inter-packet interval behavior matrices.
% As an example of how the linear representation allows drastically improved analysis and modeling of network traffic, we apply non-negative matrix factorization to find an low-dimensional representation of packet size and inter-packet flow behaviors.
% Each flow's behavior can be explained as a linear combination of only twelve ``basic behaviors.'' 
% Although they are found purely algorithmically from packet size and inter-packet interval distributions, these behaviors correspond to intuitive mode of network activity.
This factorization extracts a small set of ``basic behaviors'' from a traffic matrix and simultaneously explains each flow's observed behavior as a mixture of these basic behaviors.
Although the basic behaviors are found without examining port numbers or protocols, they nevertheless correspond to intuitive network activities such as file transfer, typing via \caps{SSH}, web surfing, and ping traffic.

@@

The rest of the paper is organized as follows. In \Section{motivation} we discuss motivation and related work. The notion of linear representation and the general matrix model are presented in \Section{general-matrix-model}. In Sections~\ref{sec:common-properties}~and~\ref{sec:modeling-concepts} we explore how common network properties and modeling concepts can be expressed in the the \caps{GMM} framework. Our experimental and analytical methodology for evaluating traffic models is presented in \Section{methodology}, while the results of our experiments are explained and analyzed in \Section{results}. The ramifications of these results are discussed in \Section{discussion}. Finally, in \Section{conclusions}, we conclude with a discussion of how this research may be applied to current wireless studies. %, and how it points the way to better traffic models for the future.

@@

The interaction of network users and application behavior with the lower layers of the networking stack is characterized by where, when, how much, and to whom data is transmitted. The joint pattern of traffic generation and mobility through time and space completely determines the effect of wireless usage on the lower levels of the network. This is due to the data-agnostic nature of the protocol stack: by design, \caps{IP} networks treat all data in the same manner~\cite{Clark88}.\QoSnote The credibility of conclusions derived from simulation or experimental deployment depends crucially on our confidence that the models used to generate traffic in experiments are sufficiently realistic. \Figure{trace-vs-uniform} demonstrates how drastically different network traffic appears under uniformity assumptions at the node, flow and packet level of behavior. Marginality assumptions are not as visually dramatic, but we will demonstrate that they distort the performance characteristics of networks almost as much, and sometimes more, than uniform models.

Paxson and Floyd observed~\cite{Paxson95} that the interplay between endpoint behavior and the network conditions is inherently \textit{closed-loop} in the sense that it is potentially affected by complex feedback. Traffic models typically attempt to preserve the closed-loop behavior of network traffic. Characterizing and modeling the feedback between the network and applications using \caps{TCP} is precisely the subject of Hern\'andez-Campos's dissertation~\cite{Hernandez06:dissertation}. Hern\'andez-Campos's addresses in great depth how to abstract an application's behavior from a \caps{TCP} trace and replay it in a manner that accurately reflects how most common applications \emph{would} react in response to other network conditions. This research has subsequently been turned into a \caps{TCP} flow generation tool for \caps{NS-2}, called \tmix~\cite{Weigle06}. It is important to note that {\tmix} does not provide models for application behavior or for mixtures of applications in networks. Rather, it provides the ability to reproduce accurate closed-loop dynamics for a single \caps{TCP} flow \emph{given} an application behavior model as input. Our work complements this perfectly: it provides the means to analyze traffic and generate realistic multi-flow application workloads which can then serve as the necessary input to \tmix.

% This presents a fundamental difficulty, however, in that it presumes that we know the intent of endpoints: what \textit{would} they have done under different conditions? While we can speculate about what an individual node might hypothetically do, we currently hardly understand the impact of the full-network traffic pattern upon performance metrics at all---even without trying to account for hypothetical reactions to alternate situations. A fuller understanding of total network behavior must be reached before we can sensibly tackle the complexities of application and user feedback.

% Although we do not attempt to model application and user feedback, we do simulate the effect of the network layer and below on the dynamics of \caps{TCP} for flows that were originally transmitted using \caps{TCP}. Hern\'andez-Campos~\cite{Hernandez06:dissertation} addresses in great depth how to abstract an application's behavior from a \caps{TCP} trace and replay it in a manner that accurately reflects how many common applications would react in response to network conditions. This research has subsequently been turned into a \caps{TCP} flow generation tool for \caps{NS-2}, called \tmix~\cite{Weigle06}. This work is complementary to ours: {\tmix} does not provide a model for application behaviors; it only provides the ability to reproduce accurate closed-loop dynamics given an accurate application behavior model. Our work our work provides the means to analyze traffic and generate realistic application workloads which can then serve as the required inputs to \tmix.

% This paper attempts to provide a first-order approximation of complete network behavior by studying the response of performance metrics to \textit{open-loop} traffic models without feedback from the network to applications and users. It is important to realize that while this does not provide a final picture, we currently lack even a first-order understanding of the effect of different workloads on performance. This first-order understanding is an essential initial step.

@@

The simplifying assumptions made by most traffic models can be classified into three categories. We use the terms \textit{uniformity}, \textit{marginality}, and \textit{regularity} to describe these classes of assumptions. They are all assumptions about the ``sameness'' of aspects of network behaviors; they differ, however, in whether the make stipulations about uniformity within each flow, across all flows, or within groups of flows. In the following sections, we explore how various modeling concepts can be expressed in the framework of the general matrix model. Models are expressed as transformations that will convert arbitrary traffic matrix instances into similar ones that satisfy the model's assumptions. These transformations will later allow us to evaluate the effect of each model's simplifications on the realism of generated workloads.

@@

%How do marginal models translate into the algebraic language of the general matrix model? Whereas uniformity assumptions for nodes,

@@

The first model we evaluate is the general matrix model itself. We derive the matrix representation directly from the trace data and use it to generate workload as described in \Section{traffic-generation}. This serves to test whether the \caps{GMM} is sufficiently general: if it accurately reproduces all performance metrics across the collection of scenarios simulated, this provides strong evidence that \caps{GMM} captures enough of the detail of trace behavior to be considered a sufficiently general representation of network traffic patterns. %An affirmation of the generality of the \caps{GMM} acts as reduction of the

@@

%The original trace traffic serves as a control group against which to compare all other models. Before we can evaluate the general matrix model (\caps{GMM}), we must establish that one potentially important aspect of traffic behavior that is \textit{not} represented in the \caps{GMM} can legitimately be discarded. That aspect of behavior is \textit{\caps{TCP} feedback}. The \caps{GMM} does not specify the \caps{IP} protocol type of each flow. Therefore we must establish the extent to which using \caps{UDP} flows, without reliable delivery or congestion control, affects performance metrics.
%%\caps{GMM} also does not indicate which flows are paired with each other in a client-server relationship. While this pairing does not affect non-\caps{TCP} flows, we implement.
%Other synthetic models derived from algebraic transformations of the \caps{GMM} are listed in \Table{traffic-models}.

@@

Our general methodology is to compare performance metrics in simulations using real traffic patterns from traces to the same metrics in simulations using a variety of trace-based models and synthetic traffic models defined using the general matrix model. We use a 24-hour trace recorded in an infrastructured 802.11g wireless \caps{LAN} with 18 access points, deployed at the 60th Internet Engineering Task Force meeting (\caps{IETF}60), held in San Diego during August of 2004. The traffic trace was captured using \texttt{\small{tcpdump}} at a single router, through which all wireless traffic for the meeting was routed, including traffic between wireless nodes. The snap length of the capture was 100 bytes, allowing \caps{IP}, \caps{ICMP}, \caps{UDP} and \caps{TCP} headers to be analyzed. We limit our work to the 24-hour sub-trace recorded on Wednesday, August 4th. This trace contains a broad variety of behaviors and entails a very large volume of traffic: 2.1 million flows, 58 million packets, and 52 billion bytes.
% 2,085,563 flows, 58,377,994 packets of application data, and 51,988,245,537 bytes of application data.

@@

What would better traffic models look like? How can we create them? One possible approach is to use actual traffic traces as we have done. This approach is unsatisfactory, however, because it provides the experimenter with almost no control over experiments. Synthetic models have parameters, which can be tweaked as necessary---adjusting, for example, the number of active nodes in a simulation, without affecting other parameters. Traffic traces, on the other hand, must be used without significant alteration if they are to actually provide the desired realism. This inability to control all but one or two parameters is nearly crippling for experimental purposes. Therefore, the research community needs models whose parameters can be adjusted independently, but whose performance characteristics can be made to resemble whatever example of network behavior one might need. The general matrix model does not yet fulfill this role since its parameters cannot be freely varied. We believe, however, that \caps{GMM} plays a vital role in the ongoing process of developing  of better models. By reducing the general problem of traffic modeling to the domain of linear algebra, we have provided traffic researchers with a vast array of powerful theoretical and computational tools that can be immediately applied to the problem at hand.\footnote{The derived models used in this paper were all implemented in Matlab, each in only a few simple lines. All the models used here are implemented in only 19 total lines of code. Of course, the framework to apply them to traffic traces and simulations is somewhat larger.} What are the next steps? The authors are currently investigating a variety of matrix factorization and clustering techniques to extract hidden structure from a large and diverse body of real traffic.

@@

We have presented a fundamentally new, algebraic way of representing traffic patterns in local area networks. We call this representation the general matrix model. Each flow of a traffic collection is represented as a single high-dimensional vector with components representing the \caps{IP} protocol type, source and destination nodes, start time, flow size, and packet behavior. The essential property of the algebraic representation is that standard vector operations compute natural and useful descriptions of aggregate behavior over the collection of flows represented. Our experimental validation demonstrates clearly that the general matrix model accurately reproduces the performance characteristics of of real traffic. The benefits of a performance-preserving algebraic representation are multifold. The algebraic forms of the simplifying assumptions made by many common modeling approaches provide unprecedented clarity and coherence to a complex and confusing subject. For example, assumptions that various aspects of flow behavior are stochastically or deterministically uniform all take the same form algebraically: left matrix multiplication. The other major class of common simplifying assumptions made by traffic models is to apply some marginal behavior across the entire collection of flows or to disjoint subsets of the flows. Such simplifications correspond to right matrix multiplication in \caps{GMM}. Because of the simplicity and clarity that the algebraic structure brings to the subject, we can see clearly now that both common types of simplifying assumptions are na\"ive and simplistic. Our experimental results bolster this conclusion: both uniform and marginal models significantly misrepresent many important network performance metrics. With the general matrix model, however, we stand poised to use the powerful tools of modern linear algebra to develop general, elegant and powerful models of network behavior that just work.

### 2008-06-04 trace_vs_uniform.tex
Work on related work & motivation.

\begin{figure*}[!t]
\begin{center}
\subfloat[node trace]
{\includegraphics[width=1.335in]{flow_topology_trace}\label{fig:flow-topology-trace}}
\subfloat[node uniform]
{\includegraphics[width=1.335in]{flow_topology_uniform}\label{fig:flow-topology-uniform}}
\subfloat[flow trace]
{\includegraphics[width=1.335in]{flow_behavior_trace}\label{fig:flow-behavior-trace}}
\subfloat[flow uniform]
{\includegraphics[width=1.335in]{flow_behavior_uniform}\label{fig:flow-behavior-uniform}}
\subfloat[packet]
{\includegraphics[width=1.335in]{flow_packet_behavior}\label{fig:packet-behavior}}
\caption{Examples illustrating trace (real) versus uniform (na\"ive synthetic) behaviors at the node, flow and packet levels. Figures \ref{fig:flow-topology-trace} and \ref{fig:flow-topology-uniform} show example node behaviors. The width of each line is proportional to the logarithm of the number of flows between the nodes it connects (zero is the Internet gateway). Uniform and trace flow behavior examples are plotted in Figures \ref{fig:flow-behavior-trace} and \ref{fig:flow-behavior-uniform}. The time axis indicates when flows start and end; the width of each flow line is proportional to the logarithm of its data rate. Figure \ref{fig:packet-behavior} compares uniform (i.e. \caps{CBR}) packet behavior with the trace of an actual flow. In the uniform model, the cumulative data sent increases smoothly over time, whereas in the actual packet trace, the transmissions are variable both in size and in inter-packet interval, leading to a ``lumpy'' cumulative data plot.}
\label{fig:trace-vs-uniform}
\end{center}
\vspace{-1.25em}
\end{figure*}

>>>>

%!TEX root = /Users/stefan/projects/papers/paper.4/paper.tex
\begin{figure*}[!t]
\begin{center}
\subfloat[node real]
{\includegraphics[width=1.335in]{flow_topology_trace}\label{fig:flow-topology-trace}}
\subfloat[node uniform]
{\includegraphics[width=1.335in]{flow_topology_uniform}\label{fig:flow-topology-uniform}}
\subfloat[flow real]
{\includegraphics[width=1.335in]{flow_behavior_trace}\label{fig:flow-behavior-trace}}
\subfloat[flow uniform]
{\includegraphics[width=1.335in]{flow_behavior_uniform}\label{fig:flow-behavior-uniform}}
\subfloat[packet]
{\includegraphics[width=1.335in]{flow_packet_behavior}\label{fig:packet-behavior}}
\caption{Examples illustrating real versus uniform behaviors at the node, flow and packet levels. Figures \ref{fig:flow-topology-trace} and \ref{fig:flow-topology-uniform} show example node behaviors. The width of each line is proportional to the logarithm of the number of flows between the nodes (zero is the Internet gateway). Uniform and trace flow behavior examples are plotted in Figures \ref{fig:flow-behavior-trace} and \ref{fig:flow-behavior-uniform}. The time axis indicates when flows start and end; the width of each flow line is proportional to the logarithm of its data rate. Figure \ref{fig:packet-behavior} compares uniform (i.e. \caps{CBR}) packet behavior with the trace of an actual flow. In the uniform model, the cumulative data sent increases smoothly over time, whereas in the actual packet trace, the transmissions are variable both in size and in inter-packet interval, leading to a ``lumpy'' cumulative data plot.}
\label{fig:trace-vs-uniform}
\end{center}
\vspace{-1.25em}
\end{figure*}
